---
title: "lab2group8"
format: html
editor: visual
---

# Hanzhi

```{r}
# Load the readr package
library(readr) 

# Load the CSV file into a data frame 
drg_data <- read_csv("DRG_data.csv")  

# Display the first few rows of the data frame 
# head(drg_data)
```

## Though I am not sure if 'DRG Definition' refers DRG code, the format of the code in 'DRG Definition' match with the DRG code's format. However, there are too many different DRG codes, so the boxplot by DRG code is messy. It makes me worry that I have made a mistake. Anyway, I apply the function to a subset of the data and verified that it successfully creates a boxplot by 'DRG Definition'. I also completed the option for different payment methods, which I hope meets most of the requirements for Function 1.

```{r}
drg_data_test <- head(drg_data, 10000)
```

```{r}
# Function 1: makes a boxplot of payments by DRG code
plot_payments_by_DRG <- function(data, payment_type = c("Average Medicare Payments", "Average Total Payments", "Average Covered Charges")) {
  
  # option for the average Medicare payments, the average total payment, or the average covered charges.
  payment_column <- switch(payment_type,
                           "Average Medicare Payments" = "Average Medicare Payments",
                           "Average Total Payments" = "Average Total Payments",
                           "Average Covered Charges" = "Average Covered Charges")
  
  # Create the boxplot 
  library(ggplot2)
  ggplot(data, aes(x = `DRG Definition`, y = .data[[payment_column]])) +
    geom_boxplot() +
    labs(
      title = paste("Boxplot of", payment_type, "by DRG Code"),
      x = "DRG Code",
      y = payment_type
    ) +
    scale_x_discrete(labels = function(x) gsub("\\D.*", "", x)) + # use DRG code on x-axis
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```

```{r}
# Example usage 
plot_payments_by_DRG(drg_data_test, "Average Covered Charges")
```

```{r}
# Function 2:  calculates statistics over all of the DRG codes for average Medicare payments
calculate_DRG_stats <- function(data, stat_type = c("mean", "median", "sd")) {

  # option for calculate either the mean, median, or standard deviation of the DRG codes
  library(dplyr)
  result <- data %>%
    group_by(`DRG Definition`) %>%
    summarise(AverageMedicarePayments = .data[["Average Medicare Payments"]]) %>%
    summarise(
      stat = switch(stat_type,
                    "mean" = mean(AverageMedicarePayments, na.rm = TRUE),
                    "median" = median(AverageMedicarePayments, na.rm = TRUE),
                    "sd" = sd(AverageMedicarePayments, na.rm = TRUE))
    )
  
  return(result)
}
```

```{r}
# To calculate the mean:
calculate_DRG_stats(drg_data, "mean")
# To calculate the median:
# calculate_DRG_stats(df, "median")
# To calculate the standard deviation:
# calculate_DRG_stats(df, "sd")
```

# Yihan

```{r}
```

# Belén

```{r}
```
